---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggExametrika

<!-- badges: start -->
<!-- badges: end -->

[Exametrika](http://shojima.starfree.jp/exmk/index.htm) is a powerful tool developed by Shojima(2022) for data analysis, 
available in [Mathematica and an Excel Add-on](http://shojima.starfree.jp/tde/index.htm). 
It has been developed as an R package at
[https://kosugitti.github.io/Exametrika/](https://kosugitti.github.io/Exametrika/).
This package, ggExametrika, is built to enhance the visualization capabilities of 
Exametrika pacakge using ggplot functions. 
It integrates seamlessly with the Exametrika package, providing beautiful and 
logically arranged plots for simplified data interpretation in R.

# Reference

Shojima, Kojiro (2022) Test Data Engineering: Latent Rank Analysis, Biclustering, andBayesian Network (Behaviormetrics: Quantitative Approaches to Human Behavior, 13), 
Springer, [https://amzn.to/42eNArd](https://amzn.to/42eNArd)


## Installation

You can install the development version of ggExametrika from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kosugitti/ggExametrika")
```

## Example

In this package, you can create plots using ggplot2 directly by inputting the output results from Exametrika. The functions responsible for generating plots are named in the format plotxxx_gg. Additionally, there are options available to display multiple plots.

## plotICC_gg Example

plotICC_gg is specifically designed for the output of IRT. Below is an example code using the Exametrika package.
To run this code, you need the Exametrika package.

```{r}
library(Exametrika)
library(ggExametrika)
result.IRT <- IRT(J15S500, model = 3)
result.IRT
```

If you want to plot ICC, input the stored results directly into the plotICC_gg function. You can also specify the range of the X-axis with a vector. If no specific range is provided, it will be plotted in the range from -4 to 4, and the function will return a list.

```{r}
plots <- plotICC_gg(result.IRT) 
# If you want to specify a range, provide a vector for the xvariable argument.
# plotICC_gg(result.IRT,xvariable = c(-7, 7))
```

This way, the ICC for each item is stored in a list called plots. If you want to see the figures, you can specify it as follows. Also, if you want to draw multiple figures simultaneously, you can use the combinePlots_gg() function.

```{r}
# Draw the ICC for Item5.
plots[5]

# Output multiple plots simultaneously (default is 6). Refer to the combinePlots_gg() documentation for specifying the figures.
combinePlots_gg(plots)
```


## plotIIC_gg Example

You can also plot the Item Information Curve (IIC) similar to the plotICC_gg function. Input the output from the Exametrika package into the plotIIC_gg function as before.

```{r}
plots <- plotIIC_gg(result.IRT) 
# If you wish to specify a range, please provide a vector for the xvariable argument. The x-axis does not necessarily have to be symmetric around 0 for plotting.
# plotIIC_gg(result.IRT,xvariable = c(-5, 7))
# plotIIC_gg(result.IRT,xvariable = c(2, 9))
```


In this method, the IIC for each item is stored in a list called plots. If you want to view the figures, you can specify it as follows. Also, if you wish to draw multiple figures simultaneously, you can use the combinePlots_gg() function.

```{r}
# Draw the IIC for Item8.
plots[8]

# We will output multiple plots simultaneously (default is 6). This time, we will display 4 plots from the 8th to the 11th.
combinePlots_gg(plots, selectPlots = c(8:11))
```

## plotTIC_gg Example

You can also plot the Test Information Curve using the same procedure. Subsequent functions may have differences in their arguments, but they are generally used in the same way. If you input data into a plotting function that does not fit the model, an error will occur, so please check the compatibility between the model and the plotting function.

```{r}
plot <- plotTIC_gg(result.IRT) 
# If you wish to specify a range, please provide a vector for the xvariable argument. The x-axis does not necessarily have to be symmetric around 0 for plotting.
```

Since we are dealing with the information curve for a single test this time, only one plot will be generated.

```{r}
# Draw the IIC for Item8.
plot
```

