---
title: "Getting Started with ggExametrika"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with ggExametrika}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5
)
```

## Overview

**ggExametrika** provides ggplot2-based visualization functions for outputs from the
[exametrika](https://kosugitti.github.io/Exametrika/) package.
It covers a wide range of psychometric models including IRT, GRM, Latent Class/Rank
Analysis, Biclustering, and Bayesian Network Models.

## Installation

```{r, eval = FALSE}
# Install from GitHub
devtools::install_github("kosugitti/ggExametrika")
```

## Quick Start

```{r, eval = FALSE}
library(exametrika)
library(ggExametrika)
```

### IRT: Item Characteristic Curve (ICC)

```{r, eval = FALSE}
# Run 2PL IRT model
result_irt <- IRT(J15S500, model = 2)

# Plot ICC for all items
plots <- plotICC_gg(result_irt)
plots[[1]]  # Show first item

# Combine multiple plots in a grid
combinePlots_gg(plots, selectPlots = 1:6, ncol = 3)
```

### IRT: Item/Test Information Curve

```{r, eval = FALSE}
# Item Information Curves
iic_plots <- plotIIC_gg(result_irt)
combinePlots_gg(iic_plots, selectPlots = 1:6, ncol = 3)

# Test Information Curve
tic_plot <- plotTIC_gg(result_irt)
tic_plot

# Test Response Function
trf_plot <- plotTRF_gg(result_irt)
trf_plot
```

### GRM: Item Category Response Function (ICRF)

```{r, eval = FALSE}
# Run Graded Response Model
result_grm <- GRM(J5S1000)

# Plot ICRF for all items
icrf_plots <- plotICRF_gg(result_grm)
icrf_plots[[1]]

# GRM also supports IIC and TIC
iic_grm <- plotIIC_gg(result_grm)
tic_grm <- plotTIC_gg(result_grm)
```

### Latent Class Analysis (LCA)

```{r, eval = FALSE}
result_lca <- LCA(J15S500, ncls = 3)

# Item Reference Profile
irp_plots <- plotIRP_gg(result_lca)
combinePlots_gg(irp_plots)

# Field Reference Profile
frp_plot <- plotFRP_gg(result_lca)
frp_plot

# Test Reference Profile
trp_plot <- plotTRP_gg(result_lca)
trp_plot

# Latent Class Distribution
lcd_plot <- plotLCD_gg(result_lca)
lcd_plot

# Class Membership Profile
cmp_plot <- plotCMP_gg(result_lca)
cmp_plot
```

### Latent Rank Analysis (LRA)

```{r, eval = FALSE}
result_lra <- LRA(J15S500, nrank = 4)

# Item/Field/Test Reference Profile
irp_plots <- plotIRP_gg(result_lra)
frp_plot <- plotFRP_gg(result_lra)
trp_plot <- plotTRP_gg(result_lra)

# Latent Rank Distribution
lrd_plot <- plotLRD_gg(result_lra)
lrd_plot

# Rank Membership Profile
rmp_plot <- plotRMP_gg(result_lra)
rmp_plot
```

### Biclustering

```{r, eval = FALSE}
result_bic <- Biclustering(J15S500, nfld = 3, nrank = 4)

# Class/Rank Reference Vectors
crv_plot <- plotCRV_gg(result_bic)
crv_plot

rrv_plot <- plotRRV_gg(result_bic)
rrv_plot

# Array plot (sorted data matrix)
array_plot <- plotArray_gg(result_bic)
array_plot
```

### Bayesian Network Model (BNM) - DAG Visualization

```{r, eval = FALSE}
result_bnm <- BNM(J15S500)

# DAG visualization
dag_plot <- plotGraph_gg(result_bnm)
dag_plot
```

## Common Plot Options

Most plot functions support the following options:

| Parameter | Description | Default |
|-----------|-------------|---------|
| `title` | `TRUE` (auto), `FALSE` (none), or character string | `TRUE` |
| `colors` | Color vector for lines/bars | Colorblind-friendly palette |
| `linetype` | Line type (`"solid"`, `"dashed"`, etc.) | `"solid"` |
| `show_legend` | Show legend | `TRUE` |
| `legend_position` | `"right"`, `"top"`, `"bottom"`, `"left"`, `"none"` | `"right"` |

Example:

```{r, eval = FALSE}
plotICC_gg(result_irt,
  title = "Custom Title",
  colors = c("red", "blue"),
  linetype = "dashed",
  show_legend = FALSE
)
```

## Function Reference

### IRT (2PL, 3PL, 4PL)

| Function | Description |
|----------|-------------|
| `plotICC_gg()` | Item Characteristic Curve |
| `plotIIC_gg()` | Item Information Curve |
| `plotTIC_gg()` | Test Information Curve |
| `plotTRF_gg()` | Test Response Function |

### GRM (Graded Response Model)

| Function | Description |
|----------|-------------|
| `plotICRF_gg()` | Item Category Response Function |
| `plotIIC_gg()` | Item Information Curve (GRM) |
| `plotTIC_gg()` | Test Information Curve (GRM) |

### Latent Class/Rank Models

| Function | Description |
|----------|-------------|
| `plotIRP_gg()` | Item Reference Profile |
| `plotFRP_gg()` | Field Reference Profile |
| `plotTRP_gg()` | Test Reference Profile |
| `plotLCD_gg()` | Latent Class Distribution |
| `plotLRD_gg()` | Latent Rank Distribution |
| `plotCMP_gg()` | Class Membership Profile |
| `plotRMP_gg()` | Rank Membership Profile |

### Biclustering

| Function | Description |
|----------|-------------|
| `plotCRV_gg()` | Class Reference Vector |
| `plotRRV_gg()` | Rank Reference Vector |
| `plotArray_gg()` | Array Plot |
| `plotFieldPIRP_gg()` | Field PIRP Plot |

### DAG Visualization

| Function | Description |
|----------|-------------|
| `plotGraph_gg()` | Directed Acyclic Graph |

### Utilities

| Function | Description |
|----------|-------------|
| `combinePlots_gg()` | Arrange multiple plots in a grid |
| `LogisticModel()` | Four-parameter logistic model |
| `ItemInformationFunc()` | IRT item information function |
| `ItemInformationFunc_GRM()` | GRM item information function |
