---
title: "Plot Gallery"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  message = FALSE,
  warning = FALSE,
  eval = requireNamespace("exametrika", quietly = TRUE)
)
```

This gallery showcases every visualization function in **ggExametrika**.
Each plot is generated from real model output using the
[exametrika](https://kosugitti.github.io/Exametrika/) package.
All functions return standard ggplot objects, so you can further customize
them with `+ theme()`, `+ labs()`, etc.

## Setup

```{r setup}
library(exametrika)
library(ggExametrika)
```

## Model Fitting

We fit all models up front.

```{r model-fitting, cache = TRUE, results = "hide"}
# --- IRT (binary, 15 items, 500 students) ---
result_irt <- IRT(J15S500, model = 2)

# --- GRM (ordinal, 5 items, 1000 students) ---
result_grm <- GRM(J5S1000)

# --- LCA (binary, 15 items, 500 students, 3 classes) ---
result_lca <- LCA(J15S500, ncls = 3)

# --- LRA (binary, 15 items, 500 students, 4 ranks) ---
result_lra <- LRA(J15S500, nrank = 4)

# --- LRAordinal (ordinal, 15 items, 3810 students, 4 ranks) ---
result_lra_ord <- LRA(J15S3810, nrank = 4, dataType = "ordinal")

# --- Biclustering: binary (35 items, 515 students) ---
result_bic <- Biclustering(J35S515, nfld = 5, nrank = 6)

# --- Biclustering: ordinal (35 items, 500 students, 5 categories) ---
result_ord_bic <- Biclustering(J35S500, ncls = 5, nfld = 5)

# --- Biclustering: nominal (20 items, 600 students, 4 categories) ---
result_nom_bic <- Biclustering(J20S600, ncls = 5, nfld = 4)
```

Network models (BNM, LDLRA, LDB, BINET) require explicit graph structure
input (an igraph DAG or edge CSV file).

```{r network-model-fitting, cache = TRUE, results = "hide"}
# --- BNM (5 items, 10 students, simple DAG) ---
bnm_dag <- igraph::make_empty_graph(n = 5, directed = TRUE)
igraph::V(bnm_dag)$name <- J5S10$ItemLabel
bnm_dag <- igraph::add_edges(bnm_dag, c(1, 3, 2, 4, 3, 5))
result_bnm <- BNM(J5S10, g = bnm_dag)

# --- LDLRA (12 items, 5000 students, 3 ranks, same DAG per rank) ---
ldlra_g <- igraph::graph_from_data_frame(
  data.frame(
    from = c("Item01", "Item02", "Item03"),
    to = c("Item02", "Item03", "Item04")
  ),
  directed = TRUE
)
result_ldlra <- LDLRA(J12S5000,
  ncls = 3,
  g = list(ldlra_g, ldlra_g, ldlra_g)
)

# --- LDB (35 items, 515 students, 3 fields, 3 ranks) ---
ldb_conf <- rep(1:3, length.out = 35)
ldb_g <- igraph::graph_from_data_frame(
  data.frame(
    from = c("Field01", "Field02"),
    to = c("Field02", "Field03")
  ),
  directed = TRUE
)
result_ldb <- LDB(J35S515,
  ncls = 3, conf = ldb_conf,
  g_list = list(ldb_g, ldb_g, ldb_g)
)

# --- BINET (35 items, 515 students, 3 classes, 3 fields) ---
binet_edges <- data.frame(
  From  = c(1, 2, 1, 2, 1, 2),
  To    = c(2, 3, 2, 3, 2, 3),
  Field = c(1, 1, 2, 2, 3, 3)
)
binet_edge_file <- tempfile(fileext = ".csv")
write.csv(binet_edges, binet_edge_file, row.names = FALSE)
result_binet <- BINET(J35S515,
  ncls = 3, nfld = 3,
  conf = ldb_conf, adj_file = binet_edge_file,
  verbose = FALSE
)
unlink(binet_edge_file)
```

---

## 1. IRT Models

Item Response Theory (2PL, 3PL, 4PL) visualization for binary response data.
Data: **J15S500** (15 items, 500 students).

### plotICC_gg --- Item Characteristic Curve

Probability of a correct response as a function of ability ($\theta$).
Returns a list of plots (one per item).

```{r icc-single}
icc_plots <- plotICC_gg(result_irt)
icc_plots[[1]]
```

```{r icc-combine, fig.width = 10, fig.height = 8}
combinePlots_gg(icc_plots, selectPlots = 1:6)
```

### plotICC_overlay_gg --- ICC Overlay

All item curves overlaid on a single plot for easy comparison.

```{r icc-overlay}
plotICC_overlay_gg(result_irt)
```

### plotIIC_gg --- Item Information Curve

How precisely each item measures ability at different $\theta$ levels.

```{r iic-single}
iic_plots <- plotIIC_gg(result_irt)
iic_plots[[1]]
```

```{r iic-combine, fig.width = 10, fig.height = 8}
combinePlots_gg(iic_plots, selectPlots = 1:6)
```

### plotIIC_overlay_gg --- IIC Overlay

All item information curves on a single plot.

```{r iic-overlay}
plotIIC_overlay_gg(result_irt)
```

### plotTIC_gg --- Test Information Curve

Total test information (sum of all item information functions).

```{r tic}
plotTIC_gg(result_irt)
```

### plotTRF_gg --- Test Response Function

Expected total score as a function of ability.

```{r trf}
plotTRF_gg(result_irt)
```

---

## 2. GRM (Graded Response Model)

Visualization for ordered polytomous response data.
Data: **J5S1000** (5 items, 1000 students).

### plotICRF_gg --- Item Category Response Function

Probability of each response category as a function of ability.
Returns a list of plots (one per item).

```{r icrf-single}
icrf_plots <- plotICRF_gg(result_grm)
icrf_plots[[1]]
```

```{r icrf-combine, fig.width = 10, fig.height = 8}
combinePlots_gg(icrf_plots, selectPlots = 1:5)
```

> **Note:** `plotIIC_gg()` and `plotTIC_gg()` also accept GRM output.
> See the [Getting Started](getting-started.html) vignette for examples.

---

## 3. Latent Class / Rank Analysis

Visualization for discrete latent variable models.
Data: **J15S500** with LCA (3 classes) and LRA (4 ranks).

### plotIRP_gg --- Item Reference Profile

Probability of a correct response for each item within each latent class or rank.
Returns a list of plots (one per item).

```{r irp-single}
irp_plots <- plotIRP_gg(result_lca)
irp_plots[[1]]
```

```{r irp-combine, fig.width = 10, fig.height = 8}
combinePlots_gg(irp_plots, selectPlots = 1:6)
```

### plotFRP_gg --- Field Reference Profile

Correct response rate by field for each class/rank.
Returns a list of plots (one per field).

> **Note:** `plotFRP_gg()` requires a model with field structure
> (Biclustering, IRM, LDB, or BINET). Shown here with binary Biclustering
> on J35S515 (5 fields, 6 ranks).

```{r frp}
plotFRP_gg(result_bic)
```

### plotTRP_gg --- Test Reference Profile

Number of students and expected test score per class/rank.

```{r trp-lca}
plotTRP_gg(result_lca)
```

### plotLCD_gg --- Latent Class Distribution

Class membership distribution (LCA).

```{r lcd}
plotLCD_gg(result_lca)
```

### plotLRD_gg --- Latent Rank Distribution

Rank membership distribution (LRA).

```{r lrd}
plotLRD_gg(result_lra)
```

### plotCMP_gg --- Class Membership Profile

Membership probability profile for each student across all classes.
Returns a list of plots (one per student).

```{r cmp, fig.width = 10, fig.height = 8}
cmp_plots <- plotCMP_gg(result_lca)
combinePlots_gg(cmp_plots, selectPlots = 1:6)
```

### plotRMP_gg --- Rank Membership Profile

Membership probability profile for each student across all ranks.
Returns a list of plots (one per student).

```{r rmp, fig.width = 10, fig.height = 8}
rmp_plots <- plotRMP_gg(result_lra)
combinePlots_gg(rmp_plots, selectPlots = 1:6)
```

---

## 4. Biclustering

Biclustering simultaneously clusters items (into fields) and students
(into ranks/classes). This section covers binary, ordinal, and nominal
Biclustering visualizations.

### Binary Biclustering

Data: **J35S515** (35 items, 515 students, 5 fields, 6 ranks).

#### plotCRV_gg --- Class Reference Vector

All class profiles in a single plot with one line per class.

```{r crv}
plotCRV_gg(result_bic)
```

#### plotRRV_gg --- Rank Reference Vector

All rank profiles in a single plot with one line per rank.

```{r rrv}
plotRRV_gg(result_bic)
```

#### plotArray_gg --- Array Plot

Visualizes the data matrix as a heatmap showing the block-diagonal
structure after biclustering.

```{r array-both, fig.width = 10, fig.height = 5}
plotArray_gg(result_bic)
```

Clustered array only:

```{r array-clustered}
plotArray_gg(result_bic, Original = FALSE, Clusterd = TRUE)
```

### Ordinal Biclustering

Data: **J35S500** (35 items, 500 students, 5 categories, 5 fields, 5 classes).

#### plotFCRP_gg --- Field Category Response Profile

Category probability plot with two display styles.

Line style (default):

```{r fcrp-line}
plotFCRP_gg(result_ord_bic, style = "line")
```

Bar style:

```{r fcrp-bar}
plotFCRP_gg(result_ord_bic, style = "bar")
```

#### plotFCBR_gg --- Field Cumulative Boundary Reference

Boundary probabilities $P(Q \geq k)$ for each field across latent classes.
Ordinal Biclustering only.

```{r fcbr}
plotFCBR_gg(result_ord_bic)
```

Select specific fields:

```{r fcbr-select}
plotFCBR_gg(result_ord_bic, fields = 1:3)
```

#### plotScoreField_gg --- Expected Score Heatmap

Expected score for each field at each class/rank, displayed as a heatmap.

```{r scorefield-ord}
plotScoreField_gg(result_ord_bic)
```

### Nominal Biclustering

Data: **J20S600** (20 items, 600 students, 4 categories, 4 fields, 5 classes).

#### plotFCRP_gg (nominal)

```{r fcrp-nom}
plotFCRP_gg(result_nom_bic, style = "line")
```

#### plotScoreField_gg (nominal)

```{r scorefield-nom}
plotScoreField_gg(result_nom_bic)
```

### Polytomous stat parameter

`plotFRP_gg()`, `plotCRV_gg()`, and `plotRRV_gg()` accept a `stat` parameter
for polytomous data: `"mean"` (default), `"median"`, or `"mode"`.

```{r frp-stat, fig.width = 10, fig.height = 8}
p_mean <- plotFRP_gg(result_ord_bic, stat = "mean") +
  ggplot2::ggtitle("stat = 'mean'")
p_median <- plotFRP_gg(result_ord_bic, stat = "median") +
  ggplot2::ggtitle("stat = 'median'")
p_mode <- plotFRP_gg(result_ord_bic, stat = "mode") +
  ggplot2::ggtitle("stat = 'mode'")
gridExtra::grid.arrange(p_mean, p_median, p_mode, ncol = 2)
```

---

## 5. LRAordinal / LRArated

Polytomous Latent Rank Analysis with specialized score-level visualizations.
Data: **J15S3810** (15 items, 3810 students, 4 ranks, ordinal).

### plotScoreFreq_gg --- Score Frequency Distribution

Density distribution of scores with vertical lines at rank boundary thresholds.

```{r scorefreq}
plotScoreFreq_gg(result_lra_ord)
```

### plotScoreRank_gg --- Score-Rank Heatmap

Joint distribution of observed scores and estimated ranks.
Darker cells indicate higher frequency.

```{r scorerank}
plotScoreRank_gg(result_lra_ord)
```

### plotICRP_gg --- Item Category Reference Profile

Probability of selecting each response category across latent ranks.
Probabilities at each rank sum to 1.0.

```{r icrp}
plotICRP_gg(result_lra_ord, items = 1:4)
```

```{r icrp-more}
plotICRP_gg(result_lra_ord, items = 5:8)
```

### plotICBR_gg --- Item Category Boundary Response

Cumulative probability curves $P(\text{response} \geq k)$ for each category
boundary. LRAordinal only.

```{r icbr}
plotICBR_gg(result_lra_ord, items = 1:4)
```

---

## 6. Network Models (DAG)

Directed Acyclic Graph and network model visualizations.
All four DAG models are supported by `plotGraph_gg()`:
BNM (items), LDLRA (items per rank), LDB (fields per rank),
and BINET (classes + fields integrated).

### plotGraph_gg --- DAG Visualization

#### BNM (Bayesian Network Model)

The simplest DAG: item-to-item dependency structure.
Data: **J5S10** (5 items, 10 students).

```{r dag-bnm}
dag_bnm <- plotGraph_gg(result_bnm)
dag_bnm[[1]]
```

Different layout directions:

```{r dag-bnm-directions, fig.width = 10, fig.height = 8}
bnm_dirs <- lapply(c("BT", "TB", "LR", "RL"), function(d) {
  plotGraph_gg(result_bnm, direction = d, title = paste("BNM -", d))[[1]]
})
gridExtra::grid.arrange(grobs = bnm_dirs, ncol = 2)
```

#### LDLRA (Locally Dependent Latent Rank Analysis)

One DAG per rank, showing how item dependencies change across ranks.
Data: **J12S5000** (12 items, 5000 students, 3 ranks).

```{r dag-ldlra, fig.width = 10, fig.height = 5}
dag_ldlra <- plotGraph_gg(result_ldlra)
combinePlots_gg(dag_ldlra)
```

#### LDB (Locally Dependent Biclustering)

One DAG per rank with field-level nodes (green diamonds).
Data: **J35S515** (35 items, 515 students, 3 fields, 3 ranks).

```{r dag-ldb, fig.width = 10, fig.height = 5}
dag_ldb <- plotGraph_gg(result_ldb)
combinePlots_gg(dag_ldb)
```

#### BINET (Bicluster Network Model)

Integrated network with two node types: Class nodes (blue squares)
and Field nodes (green diamonds) as intermediates.
Data: **J35S515** (35 items, 515 students, 3 classes, 3 fields).

```{r dag-binet}
dag_binet <- plotGraph_gg(result_binet)
dag_binet[[1]]
```

With legend showing node types:

```{r dag-binet-legend}
plotGraph_gg(result_binet,
  show_legend = TRUE,
  legend_position = "right", title = "BINET with Legend"
)[[1]]
```

#### Comparing all four DAG models

```{r dag-compare, fig.width = 10, fig.height = 8}
p_bnm <- plotGraph_gg(result_bnm, title = "BNM (Items)")[[1]]
p_ldlra <- plotGraph_gg(result_ldlra, title = "LDLRA (Items)")[[1]]
p_ldb <- plotGraph_gg(result_ldb, title = "LDB (Fields)")[[1]]
p_binet <- plotGraph_gg(result_binet,
  title = "BINET (Class+Field)",
  show_legend = TRUE
)[[1]]
gridExtra::grid.arrange(p_bnm, p_ldlra, p_ldb, p_binet, ncol = 2)
```

### plotFieldPIRP_gg --- Field Parent Item Reference Profile

Shows how field performance varies based on parent field scores, for each rank.
LDB only. Returns a list of plots (one per rank).

```{r fpirp, fig.width = 10, fig.height = 5}
fpirp_plots <- plotFieldPIRP_gg(result_ldb)
combinePlots_gg(fpirp_plots)
```

### plotLDPSR_gg --- Latent Dependence Passing Student Rate

Item-level correct response rate comparing parent and child classes
at each DAG edge. BINET only. Returns a list of plots (one per edge).

```{r ldpsr}
ldpsr_plots <- plotLDPSR_gg(result_binet)
ldpsr_plots[[1]]
```

```{r ldpsr-combine, fig.width = 10, fig.height = 8}
combinePlots_gg(ldpsr_plots, selectPlots = 1:min(6, length(ldpsr_plots)))
```

---

## 7. Common Options Demo

All plot functions share a consistent set of customization options.
Every function returns a ggplot object, so you can add further layers
with standard ggplot2 syntax.

| Parameter | Type | Default | Description |
|-----------|------|---------|-------------|
| `title` | logical or character | `TRUE` | `TRUE` = auto title, `FALSE` = hidden, character = custom |
| `colors` | character vector | `NULL` | `NULL` = colorblind-friendly palette, or custom colors |
| `linetype` | character or numeric | varies | `"solid"`, `"dashed"`, `"dotted"`, etc. |
| `show_legend` | logical | varies | Show or hide the legend |
| `legend_position` | character | `"right"` | `"right"`, `"top"`, `"bottom"`, `"left"`, `"none"` |

### title

```{r opt-title, fig.width = 10, fig.height = 4}
p1 <- plotICC_overlay_gg(result_irt, items = 1:5, title = TRUE)
p2 <- plotICC_overlay_gg(result_irt, items = 1:5, title = FALSE)
p3 <- plotICC_overlay_gg(result_irt, items = 1:5, title = "My Custom Title")
gridExtra::grid.arrange(p1, p2, p3, ncol = 3)
```

### colors

```{r opt-colors}
plotICRF_gg(result_grm,
  items = 1,
  colors = c("#D81B60", "#1E88E5", "#FFC107", "#004D40", "#7B1FA2")
)
```

```{r opt-colors-crv}
plotCRV_gg(result_bic,
  colors = c(
    "steelblue", "coral", "forestgreen",
    "mediumpurple", "goldenrod", "hotpink"
  )
)
```

### linetype

```{r opt-linetype, fig.width = 10, fig.height = 4}
p1 <- plotTIC_gg(result_irt, linetype = "solid", title = "solid")
p2 <- plotTIC_gg(result_irt, linetype = "dashed", title = "dashed")
p3 <- plotTIC_gg(result_irt, linetype = "dotdash", title = "dotdash")
gridExtra::grid.arrange(p1, p2, p3, ncol = 3)
```

### show_legend and legend_position

```{r opt-legend, fig.width = 10, fig.height = 8}
p1 <- plotICC_overlay_gg(result_irt,
  items = 1:5,
  show_legend = TRUE, legend_position = "right", title = "right"
)
p2 <- plotICC_overlay_gg(result_irt,
  items = 1:5,
  show_legend = TRUE, legend_position = "bottom", title = "bottom"
)
p3 <- plotICC_overlay_gg(result_irt,
  items = 1:5,
  show_legend = TRUE, legend_position = "top", title = "top"
)
p4 <- plotICC_overlay_gg(result_irt,
  items = 1:5,
  show_legend = FALSE, title = "show_legend = FALSE"
)
gridExtra::grid.arrange(p1, p2, p3, p4, ncol = 2)
```

### Combining options

```{r opt-combined}
plotICRF_gg(result_grm,
  items = 1,
  title = "Fully Customized ICRF",
  colors = c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3", "#FF7F00"),
  linetype = "solid",
  show_legend = TRUE,
  legend_position = "bottom"
)
```

### Post-hoc ggplot2 customization

Since all functions return ggplot objects, you can add any ggplot2 layer:

```{r opt-posthoc}
plotTIC_gg(result_irt) +
  ggplot2::theme_minimal() +
  ggplot2::labs(
    subtitle = "Custom subtitle via ggplot2",
    caption = "Generated with ggExametrika"
  )
```
